Summary

### 2016-02-23 inst/examples/summary.Rmd
Finnish geoplaces added - still some places missing

---
title: "Summary"
author: "Leo Lahti and Niko Ilomäki"
date: "Feb 3, 2016"
output: markdown_document
---

@@

>>>>

---
title: "Summary"
author: "Leo Lahti and Niko Ilomäki"
date: "Feb 24, 2016"
output: markdown_document
---

@@

## Geocoordinates for publication places

Altogether ```r 100 * mean(is.na(df.preprocessed$latitude) | is.na(df.preprocessed$longitude))``` places have missing geocoordinates:

[Places with missing geocoordinates](https://github.com/rOpenGov/fennica/blob/master/inst/examples/output.tables/missing_geocoordinates.csv)
